---
title: "Sentiment_Visualization_Correlation"
author: "Merle-Sophie Wuelbers"
date: "8/6/2020"
output: html_document
---

```{r}
# Load relevant libraries
library(ggplot2)
library(jtools)
library(dplyr)
library(stringr)
library(scales)
library(lubridate)
library(wordcloud)
library(dplyr)
library(tidyr)
library(ggsave)
```


# Visualizing Sentiment 

This part requires data in the form of a data frame, with row per Reddit comment and the following columns:

1. 'Text': the cleaned text of a comment (URLs, bot comments, etc. already removed)
2. 'compound': the VADER compound sentiment score for the given comment
3. 'Created.Date': The time stamp of the comment in <date> format

To re-run the analysis, load your text data and name it 'data'.


```{r}
# Set APA theme for plots
apatheme = theme_bw()+
  theme(panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        panel.border=element_blank(),
        axis.line=element_line(),
        legend.title=element_blank(),
        axis.text.x = element_text(angle = 90), axis.text = element_text(size=10))
```


## Sentiment over time

If it is aimed at computing running correlations between two sentiment curves in the following step, add a prefix to the `sent_per_day` variable to distinguish between different data (e.g. `google_sent_per_day`). 

```{r}
# 1. Calculate mean sentiment score per day; aggregate data by day

sent_per_day <- 
  aggregate(data$compound, by=list(date=data$Created.Date), FUN=mean)
colnames(sent_per_day) <- c("date", "compound_score_mean")
```

```{r}
# 2. Plot sentiment over time 
sent_overtime <- function(df){
  ggplot(df, aes(x=date, y=compound_score_mean)) + 
    xlab("") +
    ylab("Average Compound VADER Score") +
    scale_x_date(labels = date_format("%d/%m/%y"), 
                 breaks = seq(min(df$date), max(df$date), 2)) +
    scale_y_continuous(limits = c(-0.1,+0.35)) +
    geom_smooth(method = 'loess', formula= y ~ x, se=TRUE, fullrange=FALSE,
                level=0.95, colour="white", alpha=.4, size=.5) +
    geom_line(color="black") +
    geom_hline(yintercept = 0, linetype=1, size = 0.15) +
    apatheme
}

sent_overtime(sent_per_day)
```


### Running Correlations

Compute and plot pairwise running correlations between two firms by using their aggregated datasets called ´firm_sent_per_day` as seen below.

```{r}
# Compute pairwise running correlations
G_AM <- runCor(google_sent_per_day$compound_score_mean, 
                     amazon_sent_per_day$compound_score_mean, 10)
G_F <- runCor(google_sent_per_day$compound_score_mean, 
                     facebook_sent_per_day$compound_score_mean, 10)
G_AP <- runCor(google_sent_per_day$compound_score_mean, 
                     apple_sent_per_day$compound_score_mean, 10)
AM_F <- runCor(amazon_sent_per_day$compound_score_mean, 
                     facebook_sent_per_day$compound_score_mean, 10)
AM_AP <- runCor(amazon_sent_per_day$compound_score_mean, 
                     apple_sent_per_day$compound_score_mean, 10)
F_AP <- runCor(facebook_sent_per_day$compound_score_mean, 
                     apple_sent_per_day$compound_score_mean, 10)
```

```{r}
# Create df; wide format
GAFA_correlations <- data.frame(date = google_sent_per_day$date, G_AM, G_F,
                                G_AP, AM_F, AM_AP, F_AP)
# Convert to long format
GAFA_correlations_long <- GAFA_correlations %>%
  gather(Description, PearsonsR, 
         G_AM, G_F, G_AP, AM_F, AM_AP, F_AP)

# Rename Factors
GAFA_correlations_long$Description <- 
  factor(GAFA_correlations_long$Description,
         levels = c("G_AM", "G_F", "G_AP", "AM_F", "AM_AP", "F_AP"),
         labels = c("Google & Amazon", "Google & Facebook", "Google & Apple", 
               "Amazon & Facebook", "Amazon & Apple", "Facebook & Apple"))
```

```{r}
# Specify colours
mycols <- c("#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#CC79A7")

# Plot
sentiment_correlation_plot <- 
  ggplot(GAFA_correlations_long, aes(date, y= PearsonsR, color = Description)) +
  geom_line() +
  scale_color_manual(values = mycols) + 
  ylab("Pearsron's R") +
  xlab("") +
  facet_wrap(~Description) + 
  scale_x_date(labels = date_format("%d/%m/%y"), 
                 breaks = seq(min(GAFA_correlations_long$date),
                              max(GAFA_correlations_long$date), 15)) +
  apatheme +
  theme(axis.text.x = element_text(angle = 90), 
        axis.text = element_text(size=10)) +
  theme(legend.position = "none")
sentiment_correlation_plot
```

